\subsection*{Main idea and facts}

The following summary gives the reader an overview about the EIT Project 4 FS18 called Dojo - The networked art museum. The goal of the project is to develop the electronic for an intelligent museums guide. Summarising, the main idea of the project is to realize an audio guide with a bone conductor.

\subsection*{Background}

The project is based on a bachelor thesis of a graduate of University of Applied Sciences and Arts Northwestern Switzerland HGK in Basel. The graduate, which is the client of this project has developed the idea of an intelligent museums guide and constructed its design. The part of this project is to develop the electronic, which fulfils the clients requirements.

\subsection*{Alternative}

As desired by the client the audio transmission works with a bone conductor. One alternative would be the using of ordinary headphones, but would be less hygienic than the solution with the bone conduction. Therefore, all the focus was spent on this bone conduction transmission.

\subsection*{Conclusions}

By the fact, the design of the museum guide was already set by the client, we had to choose a small $AAA$ accumulator to supply the electronic. This conclusion ends up in a short running time, which is limited to the minimum of estimated visitor time, but depends on the users behaviour.

Further the number of files that can be stored on the museums guide is limited to a small amount as the devices only supports small SD-Cards.

\subsection*{Recommendations}

All the needed hardware and software were developed and tested in this project, but not yet tested in a big environment. To bring it to the market, another project could be launched to test and verify the museums guide in a real environment to get an insight how it acts and whether it could replace the ordinary headphone solutions.

\subsection*{Key financial numbers}

The final version of prototype costs XXX.- and comes with all needed electronic and software to configure the museums guide. We estimated that the price in production would be depending on the ordered amount about XXX.- per unit.

Since this museums guide comes with all needed software to configure the museums guide, there will be no maintenance costs except of the electricity costs for loading the accumulators.